---
title: "demo_flow_for_thesis"
author: "Ncite Da Camara"
date: "08/04/2022"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r demo-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Measure run time.
#Start time.
```{r demo-time}
start_time <- Sys.time()
```
# Pipeline configuration

Aim: Generate folders for output data (e.g., a ".rds" folder), 
set file path for input data, and apply quality control checks along the way. 
This is done by reading (i.e., source) the R scripts (i.e., code) from 
two files, namely the "config.R" and "makeMetadata.R" files.

Output: The output for the two files, namely the "config.R" and 
"makeMetadata.R" files, are as follows:

##"config.R" file:
First, a ".rds" folder is created in the current working directory.
Second, set the path to raw Luminex data files and save in an object called: 
"directory_data" that will be used as the input argument (parameter) for the 
R functions called in the demoLuminexPipeline (i.e., LuminexPipeline). Please note that the object 
"directory_data" will be used as the input argument and the output object of 
the R functions called throughout the demoLuminexPipeline. Therefore, the object 
"directory_data" will change according to each step’s R functions purpose 
(accordingly).
Third, set path to md5sums file and save in an object called: 
"directory_md5sums".
Fourth, create a summary list that will serve as the final output report to the
analyst. The summary list will be saved in an object called "summaryList" and 
a .RData file called "summaryList.RData".
Fifth, read in "dataset_project.rds" file from .rds folder, if it exists and 
save it in an object called: "directory_data" in the R global environment.
Sixth, set path to metadata files saved in the "rds" folder and read in the 
metadata files.

1.	Acquire datasets:
a.	raw Luminex data
b.	Analyte reference table dataset (i.e., "analyte_synonyms.csv").
2.	Paths to datasets
a.	raw Luminex data
b.	Please note that the raw Luminex data stored in the following ways are 
accessed and imported into R by the demoLuminexPipeline:
i.	Multiple files in multiple folders according to kit used, which is the 
SUN-IRG approach.
ii.	Multiple files in a single folder (e.g., NexGen).
c.	Analyte reference table dataset 
(e.g., the synonym table called: "analyte_synonyms.csv")
3.	Paths to output files and folders:
a.	summaryList (report) 
(i.e., summaryList.RData)
b.	rds folder
i.	dataset_project.rds
ii.	filesInvalid.rds
iii.listData.rds
iv. dataset_prtcpt.rds
v. dataset_qc.rds
vi. kits_provided_detected.rds
vii. summaryList.rds

##"makeMetadata.R"
Currently metadata is made for the example data (i.e., R01AI128765, NexGen, HIV) used 
to test the demoLuminexPipeline. The R script "makeMetadata.R" is sourced after the 
above configuration step.

For future use of the demoLuminexPipeline LuminexPipeline the following 
metadata is required from the laboratory prior to data pre-processing:
1. Project description (i.e., information about the project)
2. Manifest: i) plate layout and ii) list of specimens
3. Analyte description and conversion
4. Luminex data 
a. .csv file format and .xlsx file format
b. Include all the variables
c. Consist of a standardize file name structure for raw Luminex data without 
"reruns" (i.e., "KitName_InstrumentName_RunDate_PlateNumber"), 
e.g., "HCCBP2MAG58K_BP_20180907_03.csv"
d. Consist of a standardized file name structure for raw Luminex data with 
"reruns" (i.e., "KitName_InstrumentName_RunDate_PlateNumber_<"Rerun">Number"), 
e.g., "HCCBP2MAG58K_BP_20180907_03_Rerun01.csv")
e. Additional descriptive information regarding the basis kit such as a value 
(number) [plex number, e.g., "15 plex"] and the word "plex" without 
underscores "_" should be provided 
(i.e., "KitNamePlexNumber<"plex">_InstrumentName_RunDate_PlateNumber"), 
e.g., "HCYTOMAG60K15plex_BP_202010309_04.csv".
5. Clinical data
6. md5sums file (i.e., md5sums file received from the laboratory for all the 
exported files).
7. Data dictionary (i.e., data structure and type expected)

```{r demo-loadlibs}
#Attach R package.
#Check if required R packages are installed and loaded.
#If not, install and load the required R packages.
installpak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) {
    install.packages(new.pkg, dependencies = TRUE)
  }
  sapply(pkg, require, character.only = TRUE)
}

packages <- c('tidyverse', 'devtools', 'glue', 'gsubfn', 'here', 'proto', 'english', 
              'lubridate', 'magrittr','miceadds', 'openxlsx', 'usethis', 'visdat')

installpak(packages)


#Set working directory to "code":
setwd(here::here("code"))
getwd()
```


```{r demo-loadlibs}
#Attach R package.
source("load_libraries.R")
library(devtools)
library(demoLuminexPipeline)

setwd(here("code"))

#Load all R functions (i.e., function definition files).
#Load a source package into memory (https://r-pkgs.org/package-structure-state.html?q=build#package-states, Accessed: 28 April 2022).
#load_all()
#Remove "summaryList.RData" file.
file.remove("output/summaryList.RData")


```

```{r demo-read-config}
#Source the R scripts (i.e., code) from the 
#"config.R" and "makeMetadata.R" files.
source("config_NL.R")
source("makeMetadata_NL.R")
metadata <-read_rds("rds/metadata.rds")
```
# Pipeline:  Check essential metadata

Aim:  to check that essential metadata was provided. 
If check passed, pipeline continues. 
If check fails, pipeline stops with an error message.  
Output:  

```{r no-op}
# check all metadata objects -  
# give immediate error if missing or format wrong
# STOP - how???

```
# ---------------------------------------------------------

# Pipeline:  List raw Luminex data files

Aim:  List valid and invalid raw Luminex data files (i.e., text or Excel) from 
single or multiple file directories. In addition, capture the R version 
information, the OS, and attached or loaded packages.

Output:  2 RDS files (i.e., .rds).
1. "listData.rds" file: a list of files or the directories 
(i.e., folders) under the common top level directory 
(e.g., called "Text").
2. "filesInvalid.rds" file: List invalid files.
As well as a summary list report called "summaryList.RData" that has the
' R session information of the user.

```{r demo-list-files}
#Call R function
files_list_files_in_folders(directory_data)
```

## Test

```{r demo-tmp-rds}
tmp <- list.files("rds")
#The length of the list of files in the rds folder.
length(tmp)
#Read .rds files.
# read_rds(paste("rds/", tmp[1], sep = ""))
# read_rds(paste("rds/", tmp[2], sep = ""))
```
# ---------------------------------------------------------

# Pipeline:  Check kit names in the "filenames" variable

Aim: check kit names in the "filenames" variable by comparing expected kit names 
(i.e., the standard conventional file name) with the observed kit names in the
raw Luminex data.

Output: A RDS file (i.e., "rds/kits_provided_detected.rds") and a list called: 
"summaryList.RData"  containing: Kit names expected 
(i.e., from the metadata) and the kit names provided 
(i.e., from the raw Luminex data).


```{r demo-checkkit}
# check kit names in the "filenames" variable - immediate error if expected kit names
# do not correspond with kit names in the "filenames" variable.
# STOP - how???
#Call R function.
check_kitname_errors(filelist_file = "./rds/listData.rds",
                     metadataset = metadata$kits$kits_expected)
#Load list.
load("./output/summaryList.RData")
#View kit names in the "Kits" list in "summaryList" report.
summaryList$Kits
#Remove "summaryList" report.
rm("summaryList")
```
# --------------------------------------------------------

# Pipeline:  Count the number of folders, files and files per folder of the 
#            raw Luminex data received.

Aim: Count the number of folders, files and files per folder of the raw Luminex 
data received.

Output: a list (i.e., Output report called "summaryList.RData") containing:
#' 1. the expected number of folders,
#' 2. the expected number of files,
#' 3. the observed number of folders,
#' 4. the observed number of files

```{r demo-countfoldersfiles}
#Call R function.
files_count_folders_and_files(directory_data,
                              rds_list = "./rds/listData.rds",
                              metadata_path = metadata_path)
#Load list.
load("./output/summaryList.RData")
#View "summaryList" report.
summaryList
#Remove "summaryList" report.
rm("summaryList")
```
# ----------------------------------------------------------

# Pipeline:  Import raw Luminex data (i.e., unprocessed data)

Aim: Import (i.e., read in) raw Luminex data (i.e., multiple text files) into R 
from a single directory. Create sub tables of i) average and ii) individual 
observed concentration values (i.e., "Obs Conc" variable).
Save and use the individual observed concentration values table as 
"dataset_project.rds" for further data pre-processing and analyses.

In addition, filter out observations (elements) with no ID's 
(i.e., Description) and observations with no ID's and with the "Type" 
of unknown specimen (i.e., X).

Output: RDS file: Save subset data set containing the individual observed 
concentration (i.e., "Obs Conc" variable) values for the analytes measured in the study in a RDS 
file called "dataset_project.rds".

```{r demo-readdata}
#Call R function.
getwd()
import_data(directory_data, 
            dataName = "dataset_project")
#View a list of .rds files.
list.files("./rds/")
#Read .rds file and save as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
```
# ------------------------------------------------------------

# Pipeline: Check file import

Aim: Check file import. Determine the total number of files in folder.
Change file name and kit names to lowercase and replace dash with nothing.
Sort according to kit names.

Output: First, change file names (i.e., elements) in the "FileName" variable of 
the raw Luminex data to lowercase and replace dash with nothing.
Second, change kit names in the metadata to lowercase, replace dash with 
nothing and sort.
Third, determine the total number of files in folder from the kit names 
in the metadata.

Output Report: Save the following information in the summary list report 
(i.e., "summaryList.RData"):
1. The total number files in folder.

```{r demo-checkimport}
#Read .rds (i.e., "dataset_project.rds") file of the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#Call R function
check_file_import(dataName = dataset_project,
                  metadata = metadata)
#Load list
load("./output/summaryList.RData")
#View
summaryList$Files$file_numbers
#Remove
rm("summaryList")
```

# -----------------------------------------------------------

# Pipeline: Fix file name

Aim: Standardise file name to conventional file name of the Luminex data that
should consist of 4 components (parts) (i.e., "KitName", "InstrumentName",
"RunDate", "PlateNumber") for example "HCYTOMAG60K_BP_202010309_04". For
files that do not have a rerun. Alternatively, for files that have a
rerun ("RERUN") in the file name with or without rerun number (repeats) at
the end of the file name consist of 5 components (parts) (i.e., "KitName",
"InstrumentName", "RunDate", "PlateNumber", "RERUN_RERUNNUMBER") for
example "HCYTOMAG60K_BP_202010309_RERUN_04".
However, there are cases where the basis kit name and additional
descriptive information regarding the basis kit such as a value (number)
and the word "plex" [plex number, e.g., "15 plex"] with and without
underscores "_" are provided (e.g., "HCYTOMAG60K15plex_BP_202010309_04").
Please note, the latter should be without underscores
(e.g., "HCYTOMAG60K15plex_BP_202010309_04").

Output: A .rds file called "dataset_project.rds" and a list (i.e., Output 
report called "summaryList.RData").

```{r demo-fixfilename}
#Read .rds (i.e., "dataset_project.rds") file of the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#Call R function
fix_filenames(dataName = dataset_project, 
              col = "FileName")
#Read .rds (i.e., "dataset_project.rds") file the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#Load list
load("./output/summaryList.RData")
#View
summaryList$FileNames
#Remove
rm("summaryList")
```
# -----------------------------------------------------------

# Pipeline: Check for the word "rerun" in the file name of the raw Luminex data

Aim: Check for the word "rerun" in the file name structure of the raw Luminex 
data in the "FileName" variable and Keep distinct rows 
(i.e., unique observations).

Output: Keep distinct rows (i.e., unique observations) with i) the plate number 
with the highest rerun value (maximum row) and ii) the plates that were 
not rerun.

Return a data frame (object) consisting of the plate number with the 
highest rerun value (maximum row) as well as plates that had no rerun. 
The data frame is saved in a .rds file called "dataset_project.rds" and 
a list (i.e., Output report called "summaryList.RData").

```{r demo-checkrerun}
#Read .rds (i.e., "dataset_project.rds") file of the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#Call R function
check_rerun_in_filename_structure(dataName = dataset_project)
tmp <- read_rds("./rds/dataset_project.rds")
#View
tmp
#View
unique(tmp$KitName)
#Load list
load("./output/summaryList.RData")
#View
summaryList$Files$max_platenumber_rerun
#Remove
rm("summaryList")
#Remove
rm(dataset_project)
```

# ------------------------------------------------------------

# Pipeline: Check instrument names

Aim: Check whether the instrument name of the raw Luminex data is the same as the
input instrument name (i.e., "instrument_name") in the metadata.

Output: It returns a message (printed to the screen) informing the user if the 
instrument_name is the same as the expected instrument_name, or not.

Output Report: Save the message in the summary list report
(i.e., "summaryList.RData").

```{r demo-checkinstrumentname}
#Read .rds (i.e., "dataset_project.rds") file of the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#check number of parts = redundant
#check instrument names
#Call R function
check_instrument_name(dataName = dataset_project,
                      instrument_name = metadata$tech$instrument_names)
#Load list
load("./output/summaryList.RData")
#View
summaryList$InstrumentName_errors
#Remove
rm("summaryList")
```

# ------------------------------------------------------------

# Pipeline: Check dates

Aim: Check date format in the "Date" variable

Output: A list of "Correctly parsed unique dates" and "Incorrectly parsed
dates" is returned and saved in the output report called "summaryList".

Please note, i) a warning message will be given for the 7 "element values"
that failed to parse.
ii) save correct dates and the incorrect element values in the output 
report called "summaryList".
```{r demo-checkdates}
#Call R function
check_dates_filename(dataName = dataset_project)
#Load list
load("./output/summaryList.RData")
#View
str(summaryList$Dates)
#View
summaryList$Dates
#Remove
rm("summaryList")
#Remove
rm(dataset_project)
```
# -------------------------------------------------------------

# Pipeline: # Clean variable names

Aim: Standardise all variable (column) names to lowercase and replace symbols 
with underscores as separators in the variable names. Remove white space at 
the start and end of the variable name. Discards all the variables with "NA" 
(i.e., that is NA). Also, show variables that have been removed 
(i.e., save to "summaryList"). The changes are saved in the .rds file 
called "dataset_project.rds" and in the output report called 
"summaryList.RData".

Output: A data frame \code{dataName} with all the variable names 
standardized. Changed all variable names to lowercase and 
replace symbols with underscores as separators in the variable names. 
Remove white space at the start and end of the variable name. 
Discards all the variables with "NA's" (i.e., that is NA). Also, show the
variables that have been removed.The changes are saved in the .rds file 
called "dataset_project.rds" and in the output report called 
"summaryList.RData".

```{r demo-cleancolnames}
#Read .rds (i.e., "dataset_project.rds") file of the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
tmp <- tibble(orig = names(dataset_project),
              new = NA)
#Call R function
clean_colnames(dataName = dataset_project)
#Remove
rm(dataset_project)
#Read .rds (i.e., "dataset_project.rds") file the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
tmp$new <- names(dataset_project)
#Remove
rm(dataset_project)
```

# --------------------------------------------------------------

# Pipeline: # Clean analyte names

Aim: Standardised analyte names (i.e., consensus).

Output: A data frame \code{dataName} with standardized analyte names.

Add the unique analyte names that are present in the raw Luminex
data and not present in the Analyte Reference Table to a list
called "summaryList" (i.e., "summaryList.RData"). Save the dataset
(i.e., the raw Luminex data) containing the standardized analyte
names in a .rds file called "dataset_project.rds".

```{r demo-cleananalytenames}
#Read .rds (i.e., "dataset_project.rds") file of the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#View
unique(dataset_project$analyte)

# Read in analyte reference table (i.e., "analyte_synonyms.csv").
ref <- read_delim("C:/Users/ncite/demoLuminexPipeline/demoLuminexPipeline/inst/extdata/analyte_synonyms20230525v05.csv",
                  show_col_types = FALSE)

#Call R function
clean_analyte(dataName = dataset_project)

#Read .rds (i.e., "dataset_project.rds") file the individual observed 
#concentration values table as "dataset_project" object
dataset_project <- read_rds("./rds/dataset_project.rds")
#View
unique(dataset_project$analyte_new)
#Remove
rm(dataset_project)
#Load list
load("./output/summaryList.RData")
#View
summaryList$Analytes$not_in_analyte_ref
#Remove
rm("summaryList")
```

# ---------------------------------------------------------------

# Pipeline: # Clean description names

Aim: Standardised description names (i.e., specimen ID's).
Change all the description names to lower case and replace all the 
spaces with nothing.

Output: A data frame \code{dataName} with standardized description names. All 
the description names have been changed to lower case and all the spaces 
have been replaced with nothing.

Save the dataset (i.e., the raw Luminex data) containing the 
standardized description names in a .rds file called 
"dataset_project.rds".
# ?? clean Description
# How to automate that

```{r demo-cleandescript}
#Read .rds (i.e., "dataset_project.rds") file of the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#Call R function
clean_description(dataName = dataset_project)
#Remove
rm(dataset_project)
#Read .rds (i.e., "dataset_project.rds") file the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#View
dim(dataset_project)
#Total number of distinct (i.e., unique) description names.
unique(dataset_project$description) %>% length()
```

# --------------------------------------------------------------

# Pipeline: # Remove symbols

Aim: Classify missing data and add metadata variables, as well as, remove 
symbols.

Output: A data frame (tibble) containing six new variables, namely:
meta_trueMissing, meta_ThreeStar indicating no data is present, 
meta_OneStar indicating extrapolation value, meta_OORgt indicating OOR 
greater than, meta_OORlt indicating OOR less than, and Obs.Conc.numerics
containing the observed concentration measurement (i.e., number).

The data frame is saved in a RDS file called "dataset_project.rds" 
(i.e., "rds/dataset_project.rds").

```{r demo-removesymbols}
#Read .rds (i.e., "dataset_project.rds") file of the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#Call R function
remove_symbols(dataName = dataset_project)
#Remove
rm(dataset_project)
#Read .rds (i.e., "dataset_project.rds") file the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#View
dim(dataset_project)
#View
dataset_project %>%
  select(contains("meta")) %>%
  distinct()
```

# -----------------------------------------------------------------
# Pipeline: # Check the number of analytes per kit (only), the total number of 
plates per kit (only), visualize the total number of analytes per 
kit and plate number, and the total number of analytes used in 
the study.

Aim: Count the **total number of analytes per kit (only)**, the **total number 
#    of plates per kit (only), the **total number of analytes per kit and plate 
#    number**, and the **total number of analytes** used in the study.

Output: A tibble filtered for unknown specimens (i.e., X). Containing 
i) the **total number of analytes per kit (only)**, ii) the
**total number of plates per kit (only)**, iii) figures of the
**total number of analytes per kit and plate number**, and iv) the 
**total number of analytes used in the study**. The above information 
is saved in the output report called "summaryList" 
(i.e., "summaryList.RData").

```{r demo-analytecount}
#Read .rds (i.e., "dataset_project.rds") file the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#Call R function
total_analytes_per_kit(dataName = dataset_project)
#Load list
load("./output/summaryList.RData")
#Remove
rm("summaryList")
```

# -----------------------------------------------------------------
# Pipeline: # Split the raw Luminex data set (i.e., "dataset_project.rds") into 
# quality control data set (QC) and participant data set 
# (i.e., "dataset_prtcpt.rds"). In addition, add time point information from
# the metadata file.

Aim: Split the raw Luminex data set (i.e., "dataset_project.rds") into 
# quality control data set (QC) and participant data set 
# (i.e., "dataset_prtcpt.rds"). In addition, add time point information from
# the metadata file.

Output: Two data frames from the "dataset_project" data frame, namely,
i) QC data set (i.e., "dataset_qc") and ii) participant data set
(i.e., "dataset_prtcpt") are returned. These data sets contain selected 
variables and unique rows for the participant dataset (i.e., "dataset_prtcpt") for
further data pre-processing in the demoLuminexPipeline.

The two data frames (i.e., "dataset_prtcpt" and "dataset_qc") are saved
in RDS files called "rds/dataset_project.rds" and "rds/dataset_qc.rds".

```{r demo-participant}
#Read .rds (i.e., "dataset_project.rds") file of the individual observed 
#concentration values table as "dataset_project" object.
dataset_project <- read_rds("./rds/dataset_project.rds")
#Call R function
split_qc_prtcpt(dataName = dataset_project)
#Read .rds (i.e., "dataset_project.rds") file the individual observed 
#concentration values table as "dataset_project" object.
dataset_prtcpt <- read_rds("./rds/dataset_prtcpt.rds")
#Read .rds (i.e., "dataset_qc.rds") file the qc table as "dataset_qc" object.
dataset_qc <- read_rds("./rds/dataset_qc.rds")
```
# -----------------------------------------------------------------

# Continue with the dataset_prtcpt data set (i.e., "rds/dataset_prtcpt.rds").

# ----------------------------------------------------------------
# Pipeline: # Identify and remove (delete) true duplicates.

# duplicates annotate

# Different types of duplicates:
# reruns
# technical replicates
# time points
# true duplicates

Aim: Identify and remove (delete) true duplicates, these are rows
that are repeated for the same observations (elements).

In addition, check for reruns that are not successfully excluded.
These are specimens that have the same "kitname, instrumentname, date,
platenumber, **well**, description, timepoint, stimulation, and
**analyte_new** (i.e., analyte name)" variables.

Remove duplicates from "dataset_prtcpt" data set and save in an object called
"tmp". Bind maximum rerun elements in the "tmp1" object to the "dataset_prtcpt"
data set. These are maximum rerun duplicates sliced from the "tmp" data frame
and saved in the "tmp1" data frame.

#"duplicates, Well included".
Duplicates identified for the same "Study_Group".
Add a new variable called "Duplicated_well" that will help when viewing
missing values in the dataset by filtering for the observations in the
dataset that does not have a duplicated well (i.e., no "Duplicated_well")
before applying the vis_miss() R function from the visdat R package to 
visualise missing values.

#"duplicates, technical replicates".
Identify and save all the technical replicates in an object.
Technical replicates are the same specimen (i.e., Blanks (B), Standards (S)
, Controls (QC), and Unknowns (X)) that are present on the same plate more
than once (e.g., duplicates, triplicates) of which the average (i.e., mean)
values are calculated and taken further.

#"duplicates, the same analyte in different kits".
Add a variable (i.e., "Duplicated_analyte_in_diff_kits") to indicate that
the same analyte is present in different kits in the "dataset_prtcpt"
data set.

Output: The technical replicates are saved in the output report called 
"summaryList" (i.e., "summaryList.RData").

Save the participant dataset (i.e., "dataset_prtcpt") with no duplicates
, but with technical replicates in a RDS file called 
"dataset_prtcpt.rds".

```{r demo-duplicateparticipant}
#Read .rds (i.e., "dataset_prtcpt.rds") file of the participants individual 
#observed concentration values table as "dataset_prtcpt" object.
dataset_prtcpt <- read_rds("./rds/dataset_prtcpt.rds")
#Call R function
duplicates_annotate(dataset_prtcpt = dataset_prtcpt)
#Load list
load("./output/summaryList.RData")
#View
summaryList$Observations[[1]] %>%
  filter(replicate_unexpected == "yes")
#Remove
rm("summaryList")
#Remove
rm(dataset_prtcpt)
#Read .rds (i.e., "dataset_project.rds") file the individual observed 
#concentration values table as "dataset_project" object
dataset_prtcpt <- read_rds("./rds/dataset_prtcpt.rds")
#View
dataset_prtcpt %>%
  select(description, duplicated_well, replicate_unexpected) %>%
  filter(replicate_unexpected == "yes")
```

#----------------------------------------------------------------
# Pipeline: # Visualise missingness (missing values) in the data

# Missing values

Aim: Plots of the unique participant data set and all the combinations of the
factor variables (i.e., "Timepoint" variable and "Stimulation" variable)
are generated to visualise missing data of the combinations of the factor
variables (i.e., "Timepoint" variable and "Stimulation" variable).

Determine the total number of unknown specimens (i.e., "X")
per analyte, per kit and per plate for
the actual Luminex experiment.

Determine the proportions of different types of missing values, namely: 
i) out of range less than (i.e., prop_OORlt), ii) out of range
greater than (i.e., prop_OORgt), and iii) true missing values, these are
missing values due to no read (i.e., prop_true_missing).

Output: The plots showing the missing values of the factor variables, i.e., 
"Timepoint" and the "Stimulation" condition 
(i.e., "Timepoint" variable and "Stimulation" variable) are saved in the 
output report called "summaryList" (i.e., "summaryList.RData").

A data frame (i.e., object) containing an ordered 
plot of the total number of unknown specimen (i.e., "X") per analyte, 
per kit and per plate number (i.e., design of the experiment) for the 
actual Luminex experiment is saved in the output report called 
"summaryList" (i.e., "summaryList.RData").

Additionally, a data frame (i.e., object) containing the 
proportions of the different types of missing values (i.e., prop_OORlt,
prop_OORgt, or prop_true_missing) is saved in the output report called 
"summaryList" (i.e., "summaryList.RData").

```{r demo-missingness}
#Read .rds (i.e., "dataset_prtcpt.rds") file of the participants individual 
#observed concentration values table as "dataset_prtcpt" object
dataset_prtcpt <- read_rds("./rds/dataset_prtcpt.rds")
#Call R function
visualise_na_wideformat(dataset_prtcpt = dataset_prtcpt,
                        metadataset = metadata$timepoints)
#Call R function
x_wells_per_kit_per_plate(dataset_prtcpt = dataset_prtcpt)
#Call R function
missing_proportions(dataset_prtcpt = dataset_prtcpt)
#Load list
load("./output/summaryList.RData")
#View
summaryList$Missingness
#Remove
rm("summaryList")
```
# -----------------------------------------------------------------
# Pipeline: # Impute OOR below (<) and OOR above (>) values

# Impute

Aim: Impute OOR below (<) and OOR above (>) values with a 0.0001 fraction of
the range of a particular analyte.

Output: The imputed participant data set is saved in a RDS file called:
"dataset_prtcpt.rds".

```{r demo-impute}
#Call R function
replace(dataset_prtcpt = dataset_prtcpt)
#Read .rds (i.e., "dataset_prtcpt.rds") file of the participants individual 
#observed concentration values table as "dataset_prtcpt" object
dataset_prtcpt <- read_rds("./rds/dataset_prtcpt.rds")
#View
dataset_prtcpt %>%
  select(contains("conc")) %>%
  filter(is.na(obs_conc_numerics))
```

# -------------------------------------------------------------------
# Pipeline: # Replicates collapse to mean imputed observed concentration values

# Collapse technical replicates

Aim: Determine the mean observed concentration for the replicated
imputed observed concentration values and save in a new variable 
(i.e., called "Obs_Conc_Impute").

Output: A RDS file (i.e., "rds/dataset_prtcpt_mean_conc.rds") consisting of the 
#' participant data set (i.e., "dataset_prtcpt") with the mean observed
#  concentration for the imputed observed concentration values
#  (i.e., "obs_conc_impute" variable).

```{r demo-replicates}
# collapse technical replicates
#Read .rds (i.e., "dataset_prtcpt.rds") file of the participants individual 
#observed concentration values table as "dataset_prtcpt" object
dataset_prtcpt <- read_rds("./rds/dataset_prtcpt.rds")
#Call R function
replicates_collapse(dataset_prtcpt = dataset_prtcpt)
#Read .rds (i.e., "dataset_prtcpt_mean_conc.rds") file of the participants 
#mean individual observed concentration values table as 
#"dataset_prtcpt_mean_conc" object
dataset_prtcpt_mean_conc <- read_rds("./rds/dataset_prtcpt_mean_conc.rds")
#View
dataset_prtcpt_mean_conc %>% 
  group_by(description, timepoint, analyte_new) %>% 
  count() %>% 
  filter(n != 1) %>% 
  inner_join(dataset_prtcpt_mean_conc) %>% 
  select(description, timepoint, analyte_new, instrumentname,
         kitname)
```

# -------------------------------------------------------------------

# Transformations

# later

# ---------------------------------------------------------------

# Summary stats and visualise

# ---------------------------------------------------------------

# Measure run time.
#End time.
```{r demo-time-end}
end_time <- Sys.time()
time_taken <- round(end_time - start_time,2)
time_taken
#Capture in summaryList
#Output report: Save the run time in the summary list report
#(i.e., "summaryList.RData")
load("./output/summaryList.RData")
summaryList[["RunTime"]] <- time_taken
save(summaryList, file = "./output/summaryList.RData")
```
# ---------------------------------------------------------------
# R session information

Aim: Capture the R session information, the operating system (OS) information,
and the loaded R packages information.

Output: The R session information is saved in an object called "summaryList" and 
a .RData file called "summaryList.RData".
```{r demo-sessioninfo}
#Output Report: Save the session information in the summary list report.
#(i.e., "summaryList.RData")
# load("summaryList.RData")
summaryList[["session_information"]] <- sessionInfo()
#Output Report: Save the above information that is saved in a data frame
#in the summary list report (i.e., "summaryList.RData").
save(summaryList, file = "./output/summaryList.RData")
```

# ---------------------------------------------------------------
# Pipeline: # SummaryList report (summaryList)

Aim: Document the data pre-processing steps done to the raw Luminex data in 
the demoLuminexPipeline in a list (i.e., called "summaryList") and save the steps 
as elements in the list to use as an output report, known as the 
"summaryList report". 

Output: The "summaryList report" is saved in an object called "summaryList" and 
a .RData file called "summaryList.RData".
```{r demo-save}
# ---------------------------------------------------------------
# Save summaryList according to investigation name
#investigation.
#Read .rds files.
dataset_project <- read_rds("./rds/dataset_project.rds")
dataset_prtcpt <- read_rds("./rds/dataset_prtcpt.rds")
dataset_qc <- read_rds("./rds/dataset_qc.rds")
#Write .rds files.
readr::write_rds(dataset_project, file = paste("./rds/dataset_project_", investigation, ".rds", sep = ""))
readr::write_rds(dataset_prtcpt, file = paste("./rds/dataset_prtcpt_", investigation, ".rds", sep = ""))
readr::write_rds(dataset_qc, file = paste("./rds/dataset_qc_", investigation, ".rds", sep = ""))
#Capture investigation name in summaryList
#Output report: Save the run time in the summary list report
#(i.e., "summaryList.RData")
#Remove when done (i.e., after comparing reference data with demoLuminexPipeline output: "summaryList_Levin.RData" compared with "summaryList.RData")
save(summaryList, file = sprintf("./output/summaryList_%s_%s.RData", investigation, user))
save(summaryList, file = "./output/summaryList.RData")
#.RDS file
saveRDS(summaryList, file = "./rds/summaryList.rds")
saveRDS(summaryList, file = paste("./rds/summaryList_", investigation, ".rds", sep = ""))
```

# ---------------------------------------------------------------
# Pipeline: # QC report (summaryList)

# QC report

Aim: A selection of the documented data pre-processing steps in the 
"summaryList report" is shown in the QC report. Steps (i.e., data 
pre-processing or checks) done to the raw Luminex data in the demoLuminexPipeline. 

Output: A HTML file called: "QCreport_summaryList.html" is generated and serve 
as the output report of the demoLuminexPipeline.

```{r demo-qcreport}
# QC report  (summaryList)
base_report <- "QCreport_summaryList.Rmd"
base_report1 <- base_report
base_report <- gsub("\\.Rmd", "", base_report)
base_report <- sprintf("%s_%s_%s.Rmd", base_report, investigation, user)
base_report <- sprintf("./output/%s", base_report)
#Make a copy of original .Rmd file (i.e., line 1079)
file.copy("QCreport_summaryList.Rmd", base_report, overwrite = TRUE)
#Render (i.e., Knit .Rmd file)
#rmarkdown::render(base_report)
# reportrmd <- system.file("templates", "QCreport_summaryList_R01AI128765.Rmd", package = "demoLuminexPipeline")
# file.copy(reportrmd, "QCreport_summaryList_R01AI128765.Rmd")
# rmarkdown::render("QCreport_summaryList_R01AI128765.Rmd")
reportrmd <- system.file("templates", base_report1, package = "demoLuminexPipeline")
file.copy(reportrmd, base_report)
rmarkdown::render(base_report)
```

# ---------------------------------------------------------------
# Pipeline: # Test report (summaryList)

# Test report

Aim: Generate a test report to validate the demoLuminexPipeline (i.e., automated data 
pre-processing steps done to the raw Luminex data). By comparing the 
expected vs the observed outcomes of the data pre-processing steps 
done to the raw Luminex data. 

Output: A test report in a HTML file called: "Testreport_summaryList.html" is generated that summarise i) the run time of the reference run and 
the test run by the analyst using the reference data specific to an 
investigation (e.g., R01AI128765 study).
ii) a summary table showing the match status of the data pre-processing 
steps (i.e., elements) of the reference run and the test run by the 
analyst (i.e., the status of the comparison between the whole 
reference pre-processed Luminex data set to the whole pre-processed 
Luminex data set from the analyst, study investigator, or data owner) 
using the reference data specific to an investigation 
(e.g., the R01AI128765 study).
iii) a summary table showing the data pre-processing steps (i.e., elements) 
that did not match, also known as "false outcome(s)", of the reference run 
and the test run by the analyst using reference data specific to an 
investigation (e.g., the R01AI128765 study).
iv) the status of the comparison between the pre-processed Luminex data 
sets (i.e., the reference vs the pre-processed data set by the analyst) of
1. the whole data sets, 2. the participant data sets, 3. the QC data sets, 
2. and 4. the R session information under which these data sets were ran.
v) the entire R session information of the analyst and the reference.

```{r demo-testreport-summary}
# Test report  (summaryList)
base_report <- "Testreport_summaryList.Rmd"
base_report1 <- base_report
base_report <- gsub("\\.Rmd", "", base_report)
base_report <- sprintf("%s_%s_%s.Rmd", base_report, investigation, user)
base_report <- sprintf("./output/%s", base_report) 
#Make a copy of original .Rmd file (i.e., line 1079)
file.copy("Testreport_summaryList.Rmd", base_report, overwrite = TRUE)
#Render (i.e., Knit .Rmd file)
reportrmd <- system.file("templates", base_report1, package = "demoLuminexPipeline")
file.copy(reportrmd, base_report)
rmarkdown::render(base_report)
```



