---
#title: "QC report (summaryList)"
author: "Ncite Da Camara"
date: "02/05/2022"
output: html_document
tables: true
fontsize: 12pt
---

```{r, echo=FALSE, results='asis'}
title_var <- sprintf("%s: QC report (summaryList)", investigation)
```

---
title: "`r title_var`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
#Attach R package
library(tidyverse)
library(magrittr)
library(kableExtra)
```

```{r, echo=FALSE}
#Load the summary list report (i.e., "summaryList.RData")
load("../output/summaryList.RData")
```
# Date
```{r, echo=FALSE, results='asis'}
a <- date()
```

Date: `r paste(a)`


# Run time {#runtime}
```{r, echo=FALSE, results='asis'}
a <- summaryList$RunTime
aa <- print(summaryList$RunTime)
aa <- attr(aa, "units")
```

Elapse time.
The demoLuminexPipline took `r paste(a, aa, sep = " ")` to run.

# Expected vs Observed {#expvsobs}

**Kits**

```{r, echo=FALSE, results='asis'}
# Expected vs Observed kits
number_kits <- nrow(summaryList$Kits)
```
There were `r number_kits` kits in this experiment.

This table lists the kit names provided and the kit names observed in the data files.
Please check for discrepancies.

In most cases, discrepancies are as a result of incorrectly typed file name.
For example, leaving out the letter "K" at the end of the kit name "HCYTOMAG60" 
that should be "HCYTOMAG60K" or not providing the underscore between kit name 
and additional information, i.e., "HCYTOMAG60K_RANTES" entered as 
"HCYTOMAG60KRANTES".

```{r kits expected vs observed, echo=FALSE, results='asis'}
# knitr::kable(summaryList$Kits, caption = "Kits expected vs observed.") %>% 
#   kable_styling(full_width = FALSE, position = "left")

summaryList$Kits %>% 
  knitr::kable(caption = "Kits expected vs observed.") %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")  %>% 
  kableExtra::column_spec(1, color = "black", background = ifelse(is.na(summaryList$Kits$kits_provided) == "TRUE", "red", "white"))  %>% 
  kableExtra::column_spec(2, color = "black", background = ifelse(is.na(summaryList$Kits$kits_in_filenames) == "TRUE", "red", "white"))

number_kits <- nrow(summaryList$Kits)
```

**Files**

The table is used to check that the expected number of folders and files is received from the data owner and loaded. 

The observed number of folders and files is what is in the input data folder.
The dta_files variable is derived from the file names after the raw Luminex data were imported.
Please check for discrepancies.
```{r files, echo=FALSE, results='asis'}
#Compare the expected vs observed number of folders and files.
A <- identical(summaryList$Files$file_numbers$exp_folders, summaryList$Files$file_numbers$obs_folders)
B <- identical(summaryList$Files$file_numbers$exp_nr_of_files, summaryList$Files$file_numbers$obs_nr_of_files)
C <- identical(summaryList$Files$file_numbers$exp_nr_of_plates, summaryList$Files$file_numbers$obs_nr_of_plates)

for (i in 1:length(summaryList$Files$file_numbers$exp_folders)){
  A[i] <- identical(
    summaryList$Files$file_numbers$exp_folders[i], 
    summaryList$Files$file_numbers$obs_folders[i]
  )
} 

for (i in 1:length(summaryList$Files$file_numbers$exp_nr_of_files)){
  B[i] <- identical(
    summaryList$Files$file_numbers$exp_nr_of_files[i], 
    summaryList$Files$file_numbers$obs_nr_of_files[i]
  )
}

for (i in 1:length(summaryList$Files$file_numbers$exp_nr_of_plates)){
  C[i] <- identical(
    summaryList$Files$file_numbers$exp_nr_of_plates[i], 
    summaryList$Files$file_numbers$obs_nr_of_plates[i]
  )
}

B <- summaryList$Files$file_numbers %>% 
  mutate(identical_folders = A) %>% 
  mutate(identical_nr_of_files = B) %>% 
  mutate(identical_nr_of_plates = C) 

B <- tibble(
  object = B
)

#cell (only cell of the identical column colored in).
df <- B$object 

sum_char <- function(x){
  x <- as.integer(x)
  x <- sum(x)
  return(as.character(x))
}


df2 <- tibble(
  exp_folders = "Total", 
  exp_nr_of_files = sum_char(df$exp_nr_of_files), 
  exp_nr_of_plates = sum_char(df$exp_nr_of_files), 
  obs_folders = "---", 
  obs_nr_of_files = sum_char(df$obs_nr_of_files),
  obs_nr_of_plates = sum_char(df$obs_nr_of_plates), 
  identical_folders = "---", 
  identical_nr_of_files = "---",
  identical_nr_of_plates = "---"
)

df <- df %>%
  mutate_all(as.character)

df <- bind_rows(df, df2)


df %>% 
  mutate(
    identical_folders = kableExtra::cell_spec(
      df$identical_folders, 
      color = "black", 
      background = 
        ifelse(
          df$identical_folders == 
            "FALSE",
          "red",
          "green")),
    identical_nr_of_files = kableExtra::cell_spec(
      df$identical_nr_of_files, color = "black", 
      background = 
        ifelse(
          df$identical_nr_of_files == 
            "FALSE",
          "red",
          "green")),
    identical_nr_of_plates = kableExtra::cell_spec(
      df$identical_nr_of_plates, color = "black", 
      background = 
        ifelse(
          df$identical_nr_of_plates == 
            "FALSE",
          "red",
          "green")
    )) %>% 
  kable(escape = F, booktabs = T, caption = 
          "Compare the pre-processed QC Luminex data set to the expected 
        meta dataset.", align = "lrrlrrccc") %>%
  kableExtra::kable_styling(full_width = TRUE, position = "right") %>% 
  # Format last row:
  row_spec(nrow(df), color = "black", bold = TRUE)

#OR row (entire row green)
# B$object %>% 
#   knitr::kable(caption = "Compare the pre-processed QC Luminex data set to the expected meta dataset.") %>%
#   kableExtra::kable_styling(full_width = TRUE, position = "left") %>% 
#   kableExtra::row_spec(1:nrow(B), color = "black", background = 
#                               ifelse(B$object$identical == "FALSE",
#                                      "red",
#                                      "green")
#   )
```
**New analyte names**

New analyte names that are present in the raw Luminex data and not present in the analyte reference table (i.e., "analyte_synonyms.csv").
These new analyte names should be added to the analyte reference table (i.e., "analyte_synonyms.csv") after they have been assessed and approved by the Bioinformatics group investigators.

```{r}
tmp <- summaryList$not_in_analyte_ref

if(!is.null(tmp)){
  tmp <- tibble(
  new_analyte_names <- summaryList$not_in_analyte_ref
)

tmp %>% 
  knitr::kable(caption = "New analyte names that should be added to the analyte reference table (i.e., analyte_synonyms.csv).") %>%
  kableExtra::kable_styling(full_width = TRUE, position = "left")
} else{
  print("No new analyte names identified in the raw Luminex data that is not in the analyte reference table.")
}

```
**Description**

```{r}
#Total description
tmp <- tibble(
    total_description = summaryList$Description$Total_description
)

  tmp %>% 
  knitr::kable(caption = "Total unique descriptions (i.e., specimen ID's) in the raw Luminex data.") %>%
  kableExtra::kable_styling(full_width = TRUE, position = "left") %>% 
  # Format last row:
  row_spec(nrow(tmp), color = "black", bold = TRUE)


#Description
tmp <- tibble(
  unique_description = summaryList$Description$Unique_description
)

tmp %>% 
  knitr::kable(caption = "Unique descriptions (i.e., specimen ID's) in the raw Luminex data.") %>%
  kableExtra::kable_styling(full_width = TRUE, position = "left")


```


**Experiment design**

**Total number of unknown specimens (i.e., X) per analyte, per kit and per plate**

The table shows the total number of unknown specimens (i.e., X) per analyte, per kit and per plate number.

The table also used to visualise missing unknown specimens per analyte, per kit and per plate.

On average we expect 74-76 number of measurements for the unknown specimens [excluding the Blanks (B), Controls (IQC1, IQC2, and IQC3) and Standards (S)].
If you see any entries differing from this, please discuss with the data analyst.

```{r experimentdesign, echo=FALSE, results='asis'}

# summaryList$Missingness$Xwells_per_kit_per_plate_table %>% 
#   arrange(kitname) %>% 
#   knitr::kable(caption = "Total number of unknown specimen per analyte, per kit and per plate.") %>% 
#   kable_styling(full_width = FALSE, position = "left")


#Create vector of "summaryList".
C <- summaryList

#Create vector the list "Kits" in "summaryList".
C <- C$Kits

#Transform the vector consisting of the "summaryList" list elements to a tibble.
C <- tibble(C)

#Filter for NA elemnts in "kits_provided" variable.
C <- C %>% filter(is.na(C$kits_provided) == "TRUE")

#Add a new variable called "is_na" to indicate boolean "TRUE" if NA.
C <- C %>%
  mutate(is_na = is.na(C$kits_provided))

#Rename tie column from "kits_in_filenames" to "kitname" 
#to resemble the column name in the other tibble 
#called "D <- summaryList$Kits_Analytes$Total_plates_per_kit". 
#Since these two tibbles will be joined.

C <- rename(C, kitname = kits_in_filenames)

#Create a new vector calles "D" from the emelents in the "summaryList" list.
D <- summaryList$Missingness$Xwells_per_kit_per_plate_table

#Transform the vector consisting of the "summaryList" list elements to a tibble.
D <- tibble(D)

#Join the two tibbles by "kitname".
DC <- left_join(D, C)

#Remove "kits_provided" variable.
DC <- DC %>% select(-kits_provided)

#Add boolean value to "is_na" variable (i.e., "FALSE" or "TRUE") to distinguish
#between NA or not, i.e., if the kit name in the "kitname" variable is correct 
#or has a error (i.e., "FALSE" if the kit name is correct and "TRUE" if the 
#kit name has an error).
DC <- DC %>%
  mutate(is_na = ifelse(is.na(is_na), "FALSE", "TRUE"))

#Create a table that will summarise the "Total number of unknown specimen per analyte, per kit and per plate.".
#In addition, generate red cells for the rows containing kit names with errors.
DC %>% 
  knitr::kable(caption = "Total number of unknown specimen per analyte, per kit and per plate.") %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")  %>% 
  kableExtra::column_spec(1:ncol(DC), color = "black", background = ifelse(DC$is_na == "TRUE", "red", "white"))

```
**NB! Please check before doing analyses**

Please check the missingness in the table and if it is what you expect.

Missingness can be due to a whole plate failing laboratory QC or analyte name or kit name capture error.

```{r experimentdesign02, echo=FALSE, results='asis'}

# tbl <- summaryList$Missingness$Xwells_per_kit_per_plate_table %>% 
#   arrange(kitname)
# 
# tbl <- tbl %>% 
#   anti_join(tbl[complete.cases(tbl),])
# 
# 
# tbl %>% 
#   knitr::kable(caption = "Total number of unknown specimen per analyte, per kit and per plate.") %>% 
#   kable_styling(full_width = FALSE, position = "left")
```

**Example**

**There can be different scenarios for example:**

1. Two analytes with the same name, but different kit names, and measurements not on all the plates (Example 1).

2. The analyte name is different (i.e., spelling different), however have the same kit name, and measurements not on all the plates (Example 2).
Please see example data below. 

3. Manufacturer error. For example, error made by the manufacturer including the wrong analyte in the kit (e.g., "il6" and "il6r") (Example 3). 

```{r example1, echo=FALSE, results='asis'}
#For example

df <- tibble::tibble(
analyte_new = c("ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3", "ccl3"),
kitname = c("R&D5plex", "R&D5plex", "R&D5plex", "R&D5plex", "R&D5plex", "R&D5plex", "R&D5plex", "R&D5plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex"),
plate = c("1", "2", "3", "4", "5", "6", "7", "8", "1", "2", "3", "4", "5", "6", "7", "8"),
values = c(NA, NA, NA, NA, "73", "71", NA, NA, "72", "73", "72", "71", NA, NA, "73", "73")
)

pivot_wider(df, names_from = plate, values_from = values) %>% 
  knitr::kable(caption = "Example1. Total number of unknown specimen per analyte, per kit and per plate.") %>% 
  kable_styling(full_width = FALSE, position = "left")

```

```{r example2, echo=FALSE, results='asis'}
#For example

df <- tibble::tibble(
analyte_new = c("cd40", "cd40", "cd40", "cd40", "cd40", "cd40", "cd40", "cd40", "cd40lg", "cd40lg", "cd40lg", "cd40lg", "cd40lg", "cd40lg", "cd40lg", "cd40lg"),
kitname = c("R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex"),
plate = c("1", "2", "3", "4", "5", "6", "7", "8", "1", "2", "3", "4", "5", "6", "7", "8"),
values = c("72", "73", "72", "71", NA, NA, "73", "73", NA, NA, NA, NA, "73", "71", NA, NA)
)

pivot_wider(df, names_from = plate, values_from = values) %>% 
  knitr::kable(caption = "Example2. Total number of unknown specimen per analyte, per kit and per plate.") %>% 
  kable_styling(full_width = FALSE, position = "left")

```


```{r example3, echo=FALSE, results='asis'}
#For example

df <- tibble::tibble(
analyte_new = c("il6", "il6", "il6", "il6", "il6", "il6", "il6", "il6", "il6r", "il6r", "il6r", "il6r", "il6r", "il6r", "il6r", "il6r"),
kitname = c("R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex", "R&D22plex"),
plate = c("1", "2", "3", "4", "5", "6", "7", "8", "1", "2", "3", "4", "5", "6", "7", "8"),
values = c(NA, NA, NA, NA, "73", "71", NA, NA, "72", "73", "72", "71", NA, NA, "73", "73")
)

pivot_wider(df, names_from = plate, values_from = values) %>% 
  knitr::kable(caption = "Example3. Total number of unknown specimen per analyte, per kit and per plate.") %>% 
  kable_styling(full_width = FALSE, position = "left")

```

If you see any entries differing from this, please discuss with the data analyst.

**Total distinct analytes used in the study**
```{r totalanalytesusedinthestudy, echo=FALSE}
#Total distinct analytes used in the study.
b <- summaryList$Kits_Analytes$Total_analytes_used_in_the_study

#Total analytes used in the study
#Important, the total number of analytes in the table may differ from the
#total number of analytes in the data. A reason is that the same analyte or 
#an analyte with the same name is present in different kits.
c <- sum(summaryList$Kits_Analytes$Total_analytes_per_kit$analytecount)
```

The total number of distinct analytes in the data was **`r b` analytes** and
the total analytes used in the study is **`r c` analytes**.

If this is not as expected please contact the data analyst.

**Total analytes per kit**

The table shows the total number of analytes per kit in the data.

Important, the total number of analytes in the table may differ from the
total number of distinct analytes in the data. A reason is that the same analyte 
or an analyte with the same name is present in different kits.

If this is not as expected please contact the data analyst.
```{r totalanalytesperkit, echo=FALSE, results='asis'}
# knitr::kable(summaryList$Kits_Analytes$Total_analytes_per_kit, caption = "Total analytes per kit.")  %>% 
#   kable_styling(full_width = FALSE, position = "left")

#Create vector of "summaryList".
C <- summaryList

#Create vector the list "Kits" in "summaryList".
C <- C$Kits

#Transform the vector consisting of the "summaryList" list elements to a tibble.
C <- tibble(C)

#Filter for NA elemnts in "kits_provided" variable.
C <- C %>% filter(is.na(C$kits_provided) == "TRUE")

#Add a new variable called "is_na" to indicate boolean "TRUE" if NA.
C <- C %>%
  mutate(is_na = is.na(C$kits_provided))

#Rename tie column from "kits_in_filenames" to "kitname" 
#to resemble the column name in the other tibble 
#called "D <- summaryList$Kits_Analytes$Total_plates_per_kit". 
#Since these two tibbles will be joined.

C <- rename(C, kitname = kits_in_filenames)

#Create a new vector calles "D" from the emelents in the "summaryList" list.
D <- summaryList$Kits_Analytes$Total_analytes_per_kit

#Transform the vector consisting of the "summaryList" list elements to a tibble.
D <- tibble(D)

#Join the two tibbles by "kitname".
DC <- left_join(D, C)

#Remove "kits_provided" variable.
DC <- DC %>% select(-kits_provided)

#Add boolean value to "is_na" variable (i.e., "FALSE" or "TRUE") to distinguish
#between NA or not, i.e., if the kit name in the "kitname" variable is correct 
#or has a error (i.e., "FALSE" if the kit name is correct and "TRUE" if the 
#kit name has an error).
DC <- DC %>%
  mutate(is_na = ifelse(is.na(is_na), "FALSE", "TRUE"))

DC2 <- tibble(
  kitname = "Total", 
  analytecount = sum(DC[,2]),
  is_na = "---"
)

DC <- DC %>%
  mutate_all(as.character)

DC2 <- DC2 %>%
  mutate_all(as.character)

DC <- bind_rows(DC, DC2)

#Create a table that will summarise the "Total analytes per kit.".
#In addition, generate red cells for the rows containing kit names with errors.
DC %>% 
  knitr::kable(caption = "Total analytes per kit.", align = "lrc") %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")  %>% 
  kableExtra::column_spec(1:ncol(DC), color = "black", background = ifelse(DC$is_na == "TRUE", "red", "white")) %>% 
  # Format last row:
  row_spec(nrow(DC), color = "black", bold = TRUE)
```

**Total plates per kit and instrument**
```{r}
c <- unique(summaryList$Kits_Analytes$Total_plates_per_kit$instrumentname)
```

See table to view the number of plates per kit and instrument (i.e., `r c`) in the data.

If this is not as expected please contact the data analyst.
```{r totalplatesperkitandinstrument, echo=FALSE, results='asis'}
# knitr::kable(summaryList$Kits_Analytes$Total_plates_per_kit, caption = "Total plates per kit and instrument.")  %>% 
#   kable_styling(full_width = FALSE, position = "left")

#Create vector of "summaryList".
C <- summaryList

#Create vector the list "Kits" in "summaryList".
C <- C$Kits

#Transform the vector consisting of the "summaryList" list elements to a tibble.
C <- tibble(C)

#Filter for NA elemnts in "kits_provided" variable.
C <- C %>% filter(is.na(C$kits_provided) == "TRUE")

#Add a new variable called "is_na" to indicate boolean "TRUE" if NA.
C <- C %>%
  mutate(is_na = is.na(C$kits_provided))

#Rename tie column from "kits_in_filenames" to "kitname" 
#to resemble the column name in the other tibble 
#called "D <- summaryList$Kits_Analytes$Total_plates_per_kit". 
#Since these two tibbles will be joined.

C <- rename(C, kitname = kits_in_filenames)

#Create a new vector calles "D" from the emelents in the "summaryList" list.
D <- summaryList$Kits_Analytes$Total_plates_per_kit

#Transform the vector consisting of the "summaryList" list elements to a tibble.
D <- tibble(D)

#Join the two tibbles by "kitname".
DC <- left_join(D, C)

#Remove "kits_provided" variable.
DC <- DC %>% select(-kits_provided)

#Add boolean value to "is_na" variable (i.e., "FALSE" or "TRUE") to distinguish
#between NA or not, i.e., if the kit name in the "kitname" variable is correct 
#or has a error (i.e., "FALSE" if the kit name is correct and "TRUE" if the 
#kit name has an error).
DC <- DC %>%
  mutate(is_na = ifelse(is.na(is_na), "FALSE", "TRUE"))

DC2 <- tibble(
  instrumentname = "Total",
  kitname = "---",
  platecount = sum(DC[,3]),
  is_na = "---"
)

DC <- DC %>%
  mutate_all(as.character)

DC2 <- DC2 %>%
  mutate_all(as.character)

DC <- bind_rows(DC, DC2)

#Create a table that will summarise the "Total plates per kit and instrument."
#In addition, generate red cells for the rows containing kit names with errors.
DC %>% 
  knitr::kable(caption = "Total plates per kit and instrument.", align = "llrc") %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")  %>% 
  kableExtra::column_spec(1:ncol(DC), color = "black", background = ifelse(DC$is_na == "TRUE", "red", "white")) %>% 
  # Format last row:
  row_spec(nrow(DC), color = "black", bold = TRUE)
```
**Total analytes per instrument, kit and plate number**

The total number of analytes per instrument, kit and plate number in the data are shown in table. 

If this is not as expected please contact the data analyst.

```{r totalanalytesperinstrumentkitandplatenumber, echo=FALSE, results='asis'}
# summaryList$Kits_Analytes$Total_analytes_perKit_and_PlateNumber %>% 
#   arrange(kitname) %>% 
# knitr::kable(caption = "Total analytes per instrument, kit and plate number.") %>% 
#   kable_styling(full_width = FALSE, position = "left")


#Create vector of "summaryList".
C <- summaryList

#Create vector the list "Kits" in "summaryList".
C <- C$Kits

#Transform the vector consisting of the "summaryList" list elements to a tibble.
C <- tibble(C)

#Filter for NA elemnts in "kits_provided" variable.
C <- C %>% filter(is.na(C$kits_provided) == "TRUE")

#Add a new variable called "is_na" to indicate boolean "TRUE" if NA.
C <- C %>%
  mutate(is_na = is.na(C$kits_provided))

#Rename tie column from "kits_in_filenames" to "kitname" 
#to resemble the column name in the other tibble 
#called "D <- summaryList$Kits_Analytes$Total_plates_per_kit". 
#Since these two tibbles will be joined.

C <- rename(C, kitname = kits_in_filenames)

#Create a new vector calles "D" from the emelents in the "summaryList" list.
D <- summaryList$Kits_Analytes$Total_analytes_perKit_and_PlateNumber

#Transform the vector consisting of the "summaryList" list elements to a tibble.
D <- tibble(D)

#Join the two tibbles by "kitname".
DC <- left_join(D, C)

#Remove "kits_provided" variable.
DC <- DC %>% select(-kits_provided)

#Add boolean value to "is_na" variable (i.e., "FALSE" or "TRUE") to distinguish
#between NA or not, i.e., if the kit name in the "kitname" variable is correct 
#or has a error (i.e., "FALSE" if the kit name is correct and "TRUE" if the 
#kit name has an error).
DC <- DC %>%
  mutate(is_na = ifelse(is.na(is_na), "FALSE", "TRUE"))

#Create a table that will summarise the "Total analytes per instrument, kit and plate number.".
#In addition, generate red cells for the rows containing kit names with errors.
DC %>% 
  knitr::kable(caption = "Total analytes per instrument, kit and plate number.") %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")  %>% 
  kableExtra::column_spec(1:ncol(DC), color = "black", background = ifelse(DC$is_na == "TRUE", "red", "white"))
```
**Visualise missing proportions in the data**

The table provides valuable information on the proportion of missing values according to the type of missing value [i.e., out of range (oor) less than (lt), oor greater than (gt), or true missing] per analyte in the data. The variables (i.e., columns) are labeled "prop_oorlt", "prop_oorgt", and "prop_true_missing", respectively. See table.

If this is not as expected please contact the data analyst.

Additional information is also provided such as the kit name, time point, stimulation condition, and total number of unknown specimens analysed per analyte. The variables are labeled as follows: "kitname", "analyte_new", "timepoint", "stimulation", "total", respectively. See table.

```{r visualisemissingproportionsinthedata, echo=FALSE, results='asis'}
# knitr::kable(summaryList$Missing$missing_proportions_table, caption = "Visualise missing proportions in the data.")  %>% 
#   kable_styling(full_width = FALSE, position = "left")


#Create vector of "summaryList".
C <- summaryList

#Create vector the list "Kits" in "summaryList".
C <- C$Kits

#Transform the vector consisting of the "summaryList" list elements to a tibble.
C <- tibble(C)

#Filter for NA elemnts in "kits_provided" variable.
C <- C %>% filter(is.na(C$kits_provided) == "TRUE")

#Add a new variable called "is_na" to indicate boolean "TRUE" if NA.
C <- C %>%
  mutate(is_na = is.na(C$kits_provided))

#Rename tie column from "kits_in_filenames" to "kitname" 
#to resemble the column name in the other tibble 
#called "D <- summaryList$Kits_Analytes$Total_plates_per_kit". 
#Since these two tibbles will be joined.

C <- rename(C, kitname = kits_in_filenames)

#Create a new vector calles "D" from the emelents in the "summaryList" list.
D <- summaryList$Missing$missing_proportions_table

#Transform the vector consisting of the "summaryList" list elements to a tibble.
D <- tibble(D)

#Join the two tibbles by "kitname".
DC <- left_join(D, C)

#Remove "kits_provided" variable.
DC <- DC %>% select(-kits_provided)

#Add boolean value to "is_na" variable (i.e., "FALSE" or "TRUE") to distinguish
#between NA or not, i.e., if the kit name in the "kitname" variable is correct 
#or has a error (i.e., "FALSE" if the kit name is correct and "TRUE" if the 
#kit name has an error).
DC <- DC %>%
  mutate(is_na = ifelse(is.na(is_na), "FALSE", "TRUE"))

#Create a table that will summarise the "Visualise missing proportions in the data."
#In addition, generate red cells for the rows containing kit names with errors.
DC %>% 
  knitr::kable(caption = "Visualise missing proportions in the data.") %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")  %>% 
  kableExtra::column_spec(1:ncol(DC), color = "black", background = ifelse(DC$is_na == "TRUE", "red", "white"))


tbl <- tibble::tibble(summaryList$Missing$missing_proportions_table)

tbl <- tbl %>%
  select(analyte_new, kitname, prop_oorlt, prop_oorgt, prop_true_missing)
```

**Proportion OOR less than (<) figure**
```{r}
ggplot(tbl, aes(prop_oorlt, reorder(analyte_new, prop_oorlt))) +
geom_col() +
  labs(y = "Analyte", x = "Proportion OOR <.")
```

**Proportion OOR greater than (>) figure**
```{r}
ggplot(tbl, aes(prop_oorgt, reorder(analyte_new, prop_oorgt))) +
geom_col() +
  labs(y = "Analyte", x = "Proportion OOR >.")
```

**Proportion true missingness figure**

```{r}
ggplot(tbl, aes(prop_true_missing, reorder(analyte_new, prop_true_missing))) +
geom_col() +
  labs(y = "Analyte", x = "Proportion true missingness.")
```



# Error log {#errorlog}

**Instrument name errors**

Check if  there are instrument name errors in the data.

If this is not as expected please contact the data analyst.

```{r, echo=FALSE, results='asis'}
#1. Instrument name errors
summaryList$InstrumentName_errors
```
**Dates**

Incorrectly parsed dates in the data:

```{r, echo=FALSE, results='asis'}
#2. Dates
summaryList$Dates$`Incorrectly parsed dates`
```
If this is not as expected please contact the data analyst.

# R session information {#rsessioninformation}

```{r}
summaryList$session_information
```
